Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-21 paper/sections/proof-reconstruction.tex
minor changes.

\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
0 &\text{otherwise.}
\end{cases}
\end{equation}

@@

For a more complete treatment of general recursion, and how to
define well-founded and well-structural recursive functions, we refer
the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
not only general recursion but they also treat mutual recursive
function, among other kinds.

@@

Nevertheless, \Metis does not provide neither an explanation of this
process in its \TSTP derivations nor in its documentation.
We provide such a evidence that the process of creating subgoals,
and combining them in a final conjunction proves the original goal.

>>>>

\begin{equation}
\label{eq:unshunt-rank-definition}
\unshunt_{cm}(φ)=
\begin{cases}
\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
1 &\text{otherwise.}
\end{cases}
\end{equation}

@@

For a more complete treatment of general recursion, and how to
define well-founded and well-structural recursive functions, we refer
the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
not only general recursion, but they also treat mutual recursive
function, among other kinds.

@@

Nevertheless, \Metis does not provide neither an explanation of this
process in its \TSTP derivations nor in its documentation.
We provide such an evidence that the process of creating subgoals,
and combining them in a final conjunction proves the original goal.
